\authornote{ \addORCIDlink{Jan I. Failenschmid}{0009-0007-5106-7263}

  Correspondence concerning this article should be addressed to Jan I.
  Failenschmid, Tilburg School of Social and Behavioral Sciences: Department of
  Methodology and Statistics, Tilburg University, Warandelaan 2, 5037AB
  Tilburg, Netherlands. E-mail: J.I.Failenschmid@tilburguniversity.edu

  \noindent \textbf{Data and code availability statement:} \\
  \noindent  The simulated data and code that support the findings of this
  study are available in the online supplementary material. The data
  from the Leuven Clinical Study are available upon request from the
  \href{https://emotedatabase.com/datasets/3}{EMOTE database}.

  \noindent \textbf{Disclosure of artificial intelligence-generated content
    (AIGC) tools:} \\
  \noindent The use of AIGC tools was limited to improving spelling, grammar,
  and general editing.

  \noindent \textbf{Acknowledgements:}\\
  \noindent This project was supported by a Starter Grant. Additionally, J.M.
  was supported by an ERC Consolidator Grant (101087383).

  \newpage

  \noindent \textbf{Author contribution:}\\
  \noindent \textbf{Jan I. Failenschmid}: Writing - Original Draft Preparation,
  Software, Formal Analysis, Data Curation, Conceptualization, Investigation,
  Methodology, Visualization. \textbf{Leonie V.D.E. Vogelsmeier}: Writing -
  Original Draft Preparation, Writing - Review \& Editing, Supervision,
  Conceptualization, Funding Acquisition, Project Administration,
  Investigation, Methodology. \textbf{Joris Mulder}: Writing - Review \&
  Editing, Supervision, Conceptualization, Project Administration.
  \textbf{Joran Jongerling}: Writing - Original Draft Preparation, Writing -
  Review \& Editing, Supervision, Conceptualization, Funding Acquisition,
  Project Administration, Investigation, Methodology, Formal Analysis.
}