\subsection{State Space Models}

When constructing a parametric model for time-series data, one is faced with the 
decision to model the state function globally, locally, or mixed. Global models, 
that try to capture the entire behavior of a non-linear state function, are 
oftentimes too simplistic and generalize poorly across time and individuals 
\parencite{hunter_two_2022}. Because of this, in many situations, it is easier to 
define a model in terms of a local dynamic. State space models (SSM) are a 
flexible modeling framework that combines these local dynamic models with 
measurement models, making them suitable for modeling psychological data 
\parencite{durbin_time_2012}. While SSMs formally only include lag one relationships, 
it is possible to include higher order lags by extending the 
state space \parencite{hunter_state_2018}. Further, it is possible 
to redefine the model in continuous time using differential equations. This approach is 
especially beneficial when observations are unequally spaced in time
\parencite{van_montfort_continuous_2018}.

\subsubsection{Latent Change Score Models}

Importantly, when all the dynamic equations in an SSM are linear, this modeling approach is 
very similar to estimating structural equation models with lagged variables 
\parencite{asparouhov_dynamic_2018, usami_unified_2019}. One such model is the latent change score
model (LCS), which models the amount by which the state changes as an additional latent variable. 
This latent change variable is then linearly predicted from the state value at the previous time 
point \parencite{cancer_dynamical_2021, cancer_effectiveness_2023}. Importantly, this model 
highlights how a local linear dynamic results in a global exponential 
trend. To describe this exponential trend meaningfully, the model can be parameterized in terms of an asymptote and a 
growth rate. Such that, if the growth rate is smaller than one, the state converges 
to the asymptote and if the growth rate is larger than one, it diverges. One example of a process 
that could follow such a trajectory is the developmental trajectory of intelligence, 
where one might suspect large increases in early childhood 
that level off towards an asymptote \parencite{savi_evolving_2021}.

\subsubsection{Regime Switching Models}

Another class of commonly used SSMs in psychology are regime switching models \parencite{hamaker_regime-switching_2010}.
Here one assumes that the system that underlies the time series has distinct regimes and that each 
regime is governed by a different local dynamic. To accommodate this, regime switching models 
combine multiple local models with a model for how the system switches between the regimes. 
In this way, regime switching models describe both the behavior within each regime as well as the regime switching simultaneously.
The dynamic equations are usually chosen as part of the ARIMA model family \parencite{box_time_1970}, such that only 
the parameter values of the dynamic equations change between the regimes. The regime switching is commonly modeled using 
one of two methods. First, threshold autoregressive models estimate a threshold value for one of the 
observed variables to model the regime switching \parencite{tong_threshold_1980}. 
Second, Markov switching autoregressive models use a discrete latent variable that follows a Markov chain 
to capture the regime switching \parencite{hamilton_new_1989}. One example of a process, 
in which one might reasonably suspect distinct regimes is flow, where individuals appear to
suddenly change in and out of a flow state \parencite{ceja_suddenly_2012}.
